\section{LIMITATIONS AND FUTURE ENHANCEMENTS}

\subsection{Limitations}
\begin{enumerate}
	\item The game doesn't show the player's score and highest achieved score.
	\item Both easy and hard levels have the same number of arrows, which might not suit the difficulty level.
	
	\item The game lacks a coherent storytelling and instructional guide for players.
	\item There are no shields or protective mechanisms for the player-character.
	\item The game lacks methods to restore the player's health or replenish arrows during gameplay.
	\item The absence of a comprehensive reward system, such as earning coins.
	\item The game lacks improvements or upgrades for the player's bow and arrows.
	\item The graphical user interface (GUI) is not fully immersive
\end{enumerate}



\subsection{Future Enhancements}
\begin{enumerate}
	\item New types of arrows:
	 Additional arrow varieties could be introduced, enhancing gameplay diversity and strategy. 
	\item Graphics improvement:
	 Enhancements to the game's visual elements could lead to a more immersive and appealing user experience.
	\item More difficult levels:
	 The incorporation of increasingly challenging levels would provide players with greater engagement and progression challenges.
	\item Avatar customization: 
	The addition of avatar customization options would allow players to personalize their in-game characters.
	\item  Health increment mechanism:
	 Implementing a mechanism to increase in-game health could extend gameplay and strategic options. This could be done by placing health boosters at random positions on the gamescreen.
	\item Reward system:
	 A structured reward system could motivate players by recognizing their accomplishments and fostering a sense of achievement. This may be achievedd by rewarding the player with some coins, which can be used to restore in-game health, and to purchase new and more powerful bows and arrows.
	\item Shield feature:
	 Introducing a shield mechanic could introduce a new layer of gameplay tactics and defensive strategies. This could also be done by placing shield enablers at random position in player's arena, which activates shield for a limited time period.
	\item  Enriched storytelling:
	 Enhancing the narrative elements could deepen player immersion and emotional investment in the game's world using voice records or AI generated voice of the story.
\end{enumerate}


\newpage