\newpage

\section{OBJECTIVES}
The primary objective of this project is to facilitate the practical application of the Object-Oriented Programming (OOP) model using the well-established and effective programming language, C++. The key objectives pertaining to the development of this project are outlined as follows:

\begin{enumerate}
	\item To gain a comprehensive understanding of the Object-Oriented Programming paradigm, encompassing its principles and successfully implementing them in the project.
	\item To explore the fundamental as well as advanced features offered by C++.
	\item To acquire knowledge and proficiency in designing custom header files, thereby familiarizing ourselves with the concepts of modularity and reusability.
	\item To acquire a foundational understanding of game development and testing, with a specific focus on the development of game.
	\item To become acquainted with graphics libraries such as SFML, enabling the design and implementation of a user-friendly user interface (UI).
	\item To develop a program that exhibits high performance and efficiency, taking the factors such as memory management, time constraints, algorithmic complexity, and optimal resource utilization into consideration. 
	\item To enhance our abilities in teamwork and collaborative communication, fostering effective cooperation among project members.
	
\end{enumerate}

By pursuing these objectives, we aim to gain practical knowledge and skills in OOP principles, C++ programming, modular design, game development practices, UI design, and optimization techniques. Moreover, this project serves as an opportunity to strengthen our collaborative abilities, enhancing our team dynamics and communication skills.

\newpage