	\newpage
\section{PROJECT SCOPE}
Our project involves developing an exciting game based on the character Arjun from Mahabharat. Players will control Arjun and use their mouse to shoot arrows at targets while moving in the game world.

The key aspects of the project scope include:

\begin{enumerate}
	\item User Engagement:
		We aim to create an engaging game that immerses players in the world of Arjun. By providing an enjoyable experience, we hope to entertain players and make them feel connected to the character and the epic.
	
	\item Skill Development:
	The gameplay mechanics, such as arrow shooting and precision aiming, offer players the chance to improve their hand-eye coordination, concentration, and reflexes. These skills can be valuable not just in the game, but also in real-life situations.
	
	\item Cultural Appreciation:
		Our game's theme, inspired by Mahabharat, aims to spark interest and curiosity among players who are fans of the epic or have an interest in Hindu mythology and culture. We want to contribute to cultural appreciation and raise awareness of this rich heritage.
	
	\item Learning and Engagement with Mahabharat:
	 Through the gameplay and accompanying content, we want to provide players with an opportunity to learn more about Arjun and his role in Mahabharat. By delving into the mythology, players can gain insights and develop a deeper understanding of the epic.
	 
	 \item Entertainment Industry Impact: 
	 If our game gains popularity and positive reception, it could have an impact on the entertainment industry. It may inspire similar projects and encourage the exploration of Indian mythological themes in gaming, diversifying the offerings in the industry.
\end{enumerate}


Our project aims to develop an immersive and enjoyable game centered around Arjun from Mahabharat. We want to provide players with an engaging experience, improve their skills, foster cultural appreciation, facilitate learning about Mahabharat, and potentially contribute to the broader landscape of the entertainment industry.

\pagebreak

